---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# minifyr

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

> Extremely high-speed network infrastructures are becoming more and more popular in developed countries. However, we still face crowded and low-speed Wi-Fi environments on airport, cafe, international conference, etc. Especially, a network environment of mobile devices requires efficient usage of network bandwidth.

_Empirical Study on Effects of Script Minification and HTTP Compression for Traffic Reduction_, <http://www27.cs.kobe-u.ac.jp/achieve/data/pdf/1198.pdf>

The goal of `{minifyr}` is to provide a wrapper around the `node-minify` NodeJS module.

This package bundles the whole NodeJS minifiers, so that they can be run from R. 

More background info at: [colinfay.me/node-r-package/](https://colinfay.me/node-r-package/)

## Installation

You can install the dev version of `{minifyr}` with:

``` r
remotes::install_github("colinfay/minifyr")
```

__NOTE: YOU WILL NEED NODEJS ON YOUR MACHINE__

## Example

### Install the Node deps

You'll need to run this once:

```{r eval = FALSE}
# Check node and npm are available
minifyr::node_available()
# Will install the node dependencies
minifyr::minifyr_npm_install()
```

### Note

For now, all the Node functions are called with their default arguments.

### Minifying CSS

+ [clean-css](https://github.com/jakubpawlowicz/clean-css), with `minifyr_css_cleancss()`
+ [crass](https://github.com/mattbasta/crass), with `minifyr_css_crass()`
+ [cssnano](https://github.com/cssnano/cssnano), with `minifyr_css_cssnano()`
+ [csso](https://github.com/css/csso), with `minifyr_css_csso()`
+ [sqwish](https://github.com/ded/sqwish), with `minifyr_css_sqwish()`
+ [yui](http://yui.github.io/yuicompressor/), with `minifyr_css_yui()`

### Minifying HTML

+ [html-minifier](https://github.com/kangax/html-minifier), with `minifyr_html_minifier()`

### Minify JS

+ [babel-minify](https://github.com/babel/minify), with `minifyr_js_babel()`
+ [Google Closure Compiler](https://developers.google.com/closure/compiler/), with `minifyr_js_gcc()`
+ [terser](https://github.com/terser-js/terser), with `minifyr_js_terser()`
+ [uglify-js](https://github.com/mishoo/UglifyJS2), with `minifyr_js_uglify()`
+ [YUI Compressor](http://yui.github.io/yuicompressor/), with `minifyr_js_yuiy()`

### Minify JSON

+ [jsonminify](https://github.com/babel/minify), with `minifyr_json_jsonminify()`

### Minifyr example

minifyr comes with a series of examples: 

```{r}
library(minifyr)
minifyr_example("css")
minifyr_example("html")
minifyr_example("json")
minifyr_example("js")
```

Note that files are copied to a tempfile so that you don't accidentally erase the original files.

### Example

```{bash}
echo "body {
  margin: 25px;
  background-color: rgb(240,240,240);
  font-family: arial, sans-serif;
  font-size: 14px;
}" >> "test.css"
```

```{bash}
cat test.css
```

```{r, include=FALSE}
minifyr::minifyr_css_cleancss("test.css", "test2.css")
```

```{r, eval=FALSE}
minifyr::minifyr_css_cleancss("test.css", "test2.css")
```


```{bash}
cat test2.css
```

Note that all minifiers do not minify the same way

```{r, include=FALSE}
minifyr::minifyr_css_crass("test.css", "test3.css")
```

```{r, eval=FALSE}
minifyr::minifyr_css_crass("test.css", "test3.css")
```

```{bash}
cat test3.css
```


```{bash, echo=FALSE}
rm test.css test2.css test3.css
```

